Cards persistent analysis

### 2020-01-08 cards_persistent_analysis.Rmd
Analyzing new data, and making data for generating dissertation figure

```{r}
parent_dir = "."
subdirs = c(#"results_for_humans_with_library_2", 
            "results_for_humans_with_library_3", "results_for_humans_with_library_4",
            #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4", 
            "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
            #"results_for_humans_with_library_persistent_7", 
            #"results_for_humans_with_library_persistent_8", 
            "results_for_humans_with_library_persistent_9",
            "results_for_humans_with_library_persistent_10"
            )
num_runs = 2
```

@@

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s/%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      print(filename)
      if (!file.exists(filename)) {
        print(paste("skipping ", filename, sep=""))
        next
      }
      if (grepl("config", file_type)) {
        this_d = read_config(filename)
      } else {
        this_d = read.csv(filename, check.names=F, header=T) 
        names(this_d) <- make.unique(names(this_d))

      }
      this_d = this_d %>%
        mutate(run = run_i,
               run_type = result_subdir)
      d = d %>%
        bind_rows(this_d)
    }

  }
  return(d)
}
```

```{r}
config_d = load_d(parent_dir, subdirs, num_runs, "run_config")
loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
```

@@

```{r}
loss_d = loss_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  mutate(meta = grepl("is|toggle", task)) %>%
  filter(!meta, grepl("rewards", task)) %>%
  mutate(task = sub("_rewards", "", task),
         train_or_eval = ifelse(grepl("straight_flush_l_1", task), "eval", "train"))

@@

```{r}
ggplot(loss_d,
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ meta)
```

@@

selected_meta_true_d_3 = meta_true_d %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  left_join(source_task_loss_d) %>%
  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(source_loss_and_other))
```

>>>>

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval")
language_subdirs = c("exact_eval/language")

num_runs = 5
```

@@

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = replicate(num_runs * length(result_subdirs), data.frame())
  index = 1
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s/%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      print(filename)
      if (!file.exists(filename)) {
        print(paste("skipping ", filename, sep=""))
        next
      }
      if (grepl("config", file_type)) {
        this_d = read_config(filename)
      } else {
        this_d = read.csv(filename, check.names=F, header=T) 
        names(this_d) <- make.unique(names(this_d))

      }
      this_d = this_d %>%
        mutate(run = run_i,
               run_type = result_subdir)
      d[[index]] = this_d
      index = index + 1
    }
  }
  d = bind_rows(d)
  return(d)
}
```

```{r}
config_d = load_d(parent_dir, subdirs, num_runs, "run_config")
loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
lang_d = load_d(parent_dir, language_subdirs, num_runs, "language_losses")
meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
```

@@

```{r}
loss_d = loss_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  mutate(meta = grepl("is|toggle", task)) %>%
  filter(!meta, grepl("rewards", task)) %>%
  mutate(task = sub("_expected_rewards", "", task),
         train_or_eval = ifelse(grepl("straight_flush_l_1", task), "eval", "train"))

```{r}
lang_d = lang_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  separate(task, c("task", "train_or_eval"), ":") %>%
  mutate(task = sub("_expected_rewards", "", task))

@@

```{r}
ggplot(loss_d,
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ meta)
```
```{r}
ggplot(loss_d %>%
         filter(task == "game_straight_flush_l_0_bv_0_sr_0:train"),
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ run)
```

@@

selected_meta_true_d_3 = meta_true_d %>%
  filter(epoch > 5000, epoch < 50000) %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  left_join(source_task_loss_d) %>%
  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(source_loss_and_other))
```

```{r}
# window_size = 1000
# 
# sliding_window_selected_meta_true_d = meta_true_d %>%
#   filter(epoch < 50000) %>%
#   filter(meta_task=="toggle_losers") %>%
#   mutate(source_type=case_when(
#     base_task_toe == "example_is_train" ~ "train",
#     source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
#     T ~ "eval_other")) %>%
#   group_by(run_type, run, epoch, source_type) %>%
#   summarize(mean_loss=mean(loss)) %>%
#   ungroup() %>%
#   spread(source_type, mean_loss) %>%
#   left_join(source_task_loss_d) %>%
#   mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
#   mutate(window = epoch %/% window_size) %>%
#   group_by(run_type, run, window) %>%
#   summarize(source_loss = mean(source_task_base_loss), eval_other = mean(eval_other), source_loss_and_other = mean(source_loss_and_other), eval_target = mean(eval_target)) %>%
#   ungroup() %>%
#   group_by(run_type, run) %>%
#   filter(source_loss_and_other == max(source_loss_and_other))
# sliding_window_selected_meta_true_d %>%
#   arrange(desc(source_loss_and_other))
```

# language baselines

```{r}
ggplot(lang_d,
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ run)
```

Equivalent selection for the language baselines to that used above:
```{r}
selected_lang_d = lang_d %>%
  filter(epoch > 5000,
         epoch < 50000) %>%
  mutate(task_type=case_when(
    task == "game_straight_flush_l_0_bv_0_sr_0" ~ "source",
    task == "game_straight_flush_l_1_bv_0_sr_0" ~ "eval_target",
    train_or_eval == "eval" ~ "eval_other",
    T ~ "train_other")) %>%
  group_by(run_type, run, epoch, task_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(task_type, mean_loss) %>%
  mutate(source_loss_and_other = source + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other))
selected_lang_d %>%
  arrange(desc(source_loss_and_other))
```

# data for figure

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target) %>%
  mutate(expected_reward = expected_reward / max(expected_reward))  # different scalings
```

```{r}
#write_csv()
```
